The globular cluster system of the Auriga simulations

### 2020-04-08 response_to_referee.tex

\documentclass{article}

\begin{document}

\section*{Introduction}
We thank the referee for a thoughtful and elaborate report. We address the 
comments in sections with names that match
the headings of the referee report, starting with the following listing of our 
response to the 3 paragraphs in the introduction.
\begin{enumerate}
\item We updated the abstract and conclusion to clarify that we meant to describe
what would be needed for the environmental dependence of the formation and disruption
of bound clusters for the Auriga simulations to be consistent with the observations,
rather than to argue that the Auriga simulations reflect these trends.
\item
We feel that our conclusion would be too strongly phrased if we would generalise 
our results obtained using the Auriga simulations to cosmological simulations 
in general. We find that age-selected stellar particles in the Auriga simulations 
do not reproduce key properties of observed GC systems in the Milky Way and M31.
However, our results might reflect characteristics that are specific to Auriga, 
e.g. that the galaxy formation model overmixes metals at early times. 
Therefore we did add a final bulletpoint to our conclusion to clarify the above, 
but we limit the scope to the Auriga simulations. Thanks for pointing this out!

@@

Furthermore, we clarified in the manuscript that we investigate the metallicity
and galactocentric radius because these properties are available for the observed
GC systems and in the simulations.
\item TODO: disussion of implications for wider context.
\end{enumerate}

\section*{General comments about style}
\begin{itemize}
\item Numerical quantities are now described in arabic numbers instead of words.
\item We now first use the name of the physical quantities in the given example,
    followed by the symbolic representation.
\item The text has been updated to reduce the usage of parenthesis.
\item Colloquial expressions have been rephrased.
\item We replaced `Sec.' by `Section' to refer to sections in the present work.
Moreover, we changed `Sec.' to `section' to refer to a section in one of the references.
\item All acronyms are introduced the first time they appear in the text
(MW, M31, GC, GCS, YMC, ISM, SN, AGB, DM, and Au). The subset thereof that appears 
in the abstract is also introduced the first time it appears.
\item The colour palette has been updated to improve colourblind-friendliness.
\item We no longer use blue and red to prevent confusion because they are 
typically used for metal-poor and metal-rich populations.
\end{itemize}

\section*{Major comments and concerns}
\begin{itemize}
\item TODO: add a paragraph in introduction to justify why we consider metallicity
and galactocentric radius.
\item TODO: justify age cut instead of using a more elaborate selection function.
\end{itemize}

\section*{Additional major comments}
\begin{itemize}
\item TODO justify the modelling philosophy.
\item TODO: clarify why observational data has different numbers
\item We normalise the Auriga simulations by the virial radius of the
dark matter halo to compensate for scatter between different simulation runs. We
deliberately chose for $r_{vir}$ because there are several stellar length scales
that could be used (e.g. the effective radius of the bulge, the radial scalelength
or vertical scaleheight of the disk, the optical radius, the extent of the stellar 
halo, etc). The simulations show a wide variety between properties of the Auriga
galaxies with little correlation between these different stellar length scales.
The mean virial radius of Auriga L4 is 299.67 $\pm$ 19.41 kpc. TODO
\item TODO: Discussion on the implications for the formation and evolution of clusters
    often feels a bit out of place and forced

### 2020-04-08 response_to_referee.tex

Furthermore, we clarified in the manuscript that we investigate the metallicity
and galactocentric radius because these properties are available for the observed
GC systems and in the simulations.
\item TODO: disussion of implications for wider context.
\end{enumerate}

\section*{General comments about style}
\begin{itemize}
\item Numerical quantities are now described in arabic numbers instead of words.
\item We now first use the name of the physical quantities in the given example,
    followed by the symbolic representation.
\item The text has been updated to reduce the usage of parenthesis.
\item Colloquial expressions have been rephrased.
\item We replaced `Sec.' by `Section' to refer to sections in the present work.
Moreover, we changed `Sec.' to `section' to refer to a section in one of the references.
\item All acronyms are introduced the first time they appear in the text
(MW, M31, GC, GCS, YMC, ISM, SN, AGB, DM, and Au). The subset thereof that appears 
in the abstract is also introduced the first time it appears.
\item The colour palette has been updated to improve colourblind-friendliness.
\item We no longer use blue and red to prevent confusion because they are 
typically used for metal-poor and metal-rich populations.
\end{itemize}

\section*{Major comments and concerns}
\begin{itemize}
\item TODO: add a paragraph in introduction to justify why we consider metallicity
and galactocentric radius.
\item We added section 5.3 to discuss how our results change of we adopt an age cut
of 8 or 6 Gyr.
\end{itemize}

\section*{Additional major comments}
\begin{itemize}
\item TODO justify the modelling philosophy.
\item We added a section 5.3 to discuss how our results change if we adopt an
age cut of 8 or 6 Gyr instead of 10 Gyr.
\item We clarified that the number of observed GCs differs between Figure 1 and 
Figure 2 because the latter shows metallicities between -2.5 and 0, galactocentric 
radii between 1 and 250 kpc. Figure 1, on the other hand, shows the full range
of radii, and the top panel of Figure 3 shows the full range of metallicities.
\item We normalise the Auriga simulations by the virial radius of the
dark matter halo to compensate for scatter between different simulation runs. We
deliberately chose for $r_{vir}$ because there are several stellar length scales
that could be used (e.g. the effective radius of the bulge, the radial scalelength
or vertical scaleheight of the disk, the optical radius, the extent of the stellar 
halo, the half-mass stellar radius, etc). The simulations show a wide variety 
between properties of the Auriga galaxies with little correlation between these 
different stellar length scales. Therefore we could introduce unknown biases by 
normalising to any one of these options which is why we use the virial radius instead.
\item TODO: ``Discussion on the implications for the formation and evolution of clusters
    often feels a bit out of place and forced.''

### 2020-04-08 AurigaGCS.tex
Other major comments

\subsection{Total GC mass in metallicity-radial space} 
\label{sec:observations_FeHRgc}
We show the two-dimensional mass-weighted metallicity-radial distribution of the
MW and the M31 GCS in the top and bottom panel of Figure~\ref{fig:observations_FeHRgc},
respectively. The observations indicate that
no GCs with high metallicities are to be expected at large radii (the three bins
in the upper right corner, both for MW and M31), and relatively few GCs at large
radii in general ($r_{\text{gal}} > 30$~kpc; right column: $11$ GCs or 7.3\% in
the MW and $17$ or 4.6\% in M31). Moreover, the M31 hosts more metal-rich 
([Fe/H]$ > -1$) GCs in each radial bin in comparison to the MW GCSs than what
would be expected when accounting for the fact that M31 hosts a larger GCS
than the MW. Finally, given that both marginalized (i.e. the metallicity 
and radial) distributions are not statistically consistent, we find that the 
two-dimensional distributions are also not consistent. More generally, the GCS
of the MW differs significantly from that of M31. We compare these 
observations to the Auriga simulations later on in Sec.~\ref{sec:results_FeHRgc}.

\begin{figure}
    \includegraphics[width=\columnwidth]
        {{MW_RgcFeH_HistogramMassWeighted_Harris1996ed2010data-trim}.png}
    \centering \textcolor{lightgray}{\rule[2mm]{\columnwidth}{0.05mm}}
    \includegraphics[width=\columnwidth]
        {{M31_RgcFeH_HistogramMassWeighted_CaldwellRomanowsky2016data-trim}.png}
    \caption{
        \emph{Top}: Mass-weighted $r_{\text{gal}}$-[Fe/H] distribution of
        151 GCs in the MW \citep[data from][2010 ed.]{1996AJ....112.1487H},
        color-coded by the \textbf{median} (values also shown in each bin). The 
        numbers in parenthesis show how many star particles fall within the bin.
        \emph{Bottom}: Same for M31, showing the 366 GCs in CR16 
        \citep[data from][]{2016ApJ...824...42C}. Radii of M31 are again divided by 
        $r_{\text{vir,M31}}$ and multiplied by $r_{\text{vir,MW}}$. Note that the 
        range of the colourmap differs in both figures. 
        \label{fig:observations_FeHRgc}
    }
\end{figure}

\section{Results}
\label{sec:results}
We define GC candidates in the Auriga simulations as all star particles older
than $10$~Gyr based on the age distribution of the MW GCS (top panel of 
Figure~\ref{fig:MW-M31-age-Rgc}), adopting the definition of 
\citet{2010ARA&A..48..431P} and following the method of 
\citet{2017MNRAS.465.3622R}. However, we caution that his definition does exclude 
1 GC in the MW and 24 in M31 as stated in Section~\ref{sec:age}.

@@

>>>>

\subsection{Total GC mass in metallicity-radial space} 
\label{sec:observations_FeHRgc}
We show the two-dimensional mass-weighted metallicity-radial distribution of the
MW and the M31 GCS in the top and bottom panel of Figure~\ref{fig:observations_FeHRgc},
respectively. Note that the number of GCs is different than in 
Figure~\ref{fig:MW-M31-age-Rgc} because here we plot [Fe/H] between -2.5 and 0 
and $r_{\text{gal}}$ between 1 and 250 kpc whereas Figure~\ref{fig:MW-M31-age-Rgc}
shows the full range of metallicities and radii.

The observations indicate that
no GCs with high metallicities are to be expected at large radii (the three bins
in the upper right corner, both for MW and M31), and relatively few GCs at large
radii in general ($r_{\text{gal}} > 30$~kpc; right column: $11$ GCs or 7.3\% in
the MW and $17$ or 4.6\% in M31). Moreover, the M31 hosts more metal-rich 
([Fe/H]$ > -1$) GCs in each radial bin in comparison to the MW GCSs than what
would be expected when accounting for the fact that M31 hosts a larger GCS
than the MW. Finally, given that both marginalized (i.e. the metallicity 
and radial) distributions are not statistically consistent, we find that the 
two-dimensional distributions are also not consistent. More generally, the GCS
of the MW differs significantly from that of M31. We compare these 
observations to the Auriga simulations later on in Sec.~\ref{sec:results_FeHRgc}.

\begin{figure}
    \includegraphics[width=\columnwidth]
        {{MW_RgcFeH_HistogramMassWeighted_Harris1996ed2010data-trim}.png}
    \centering \textcolor{lightgray}{\rule[2mm]{\columnwidth}{0.05mm}}
    \includegraphics[width=\columnwidth]
        {{M31_RgcFeH_HistogramMassWeighted_CaldwellRomanowsky2016data-trim}.png}
    \caption{
        \emph{Top}: Mass-weighted $r_{\text{gal}}$-[Fe/H] distribution of
        151 GCs in the MW \citep[data from][2010 ed.]{1996AJ....112.1487H},
        color-coded by the \textbf{median} (values also shown in each bin). The 
        numbers in parenthesis show how many star particles fall within the bin.
        \emph{Bottom}: Same for M31, showing the 366 GCs in CR16 
        \citep[data from][]{2016ApJ...824...42C}. Radii of M31 are again divided by 
        $r_{\text{vir,M31}}$ and multiplied by $r_{\text{vir,MW}}$. Note that the 
        range of the colourmap differs in both figures,
        \label{fig:observations_FeHRgc}
    }
\end{figure}

\section{Results}
\label{sec:results}
We define GC candidates in the Auriga simulations as all star particles older
than $10$~Gyr based on the age distribution of the MW GCS (top panel of 
Figure~\ref{fig:MW-M31-age-Rgc}), adopting the definition of a GC from
\citet{2010ARA&A..48..431P} and following the method of 
\citet{2017MNRAS.465.3622R}. However, we caution that his definition does exclude 
1 GC in the MW and 24 in M31 as stated in Section~\ref{sec:age}, and further
discuss this in Section~\ref{sec:age_min}.

@@

\subsection{Lower age cut in the GC selection function}
\label{sec:age_min}
Our method is sensitive to the definition that we adopt to classify GC candidates
\citep{2010MNRAS.404.1203F}. Therefore we explore how our results change if we 
include all star particles older than 8 Gyr, and if we further lower the age cut 
to 6 Gyr.

We find that including more recently formed star particles in our subset 
of GC candidates shifts the mean metallicity to higher values. Moreover, the
total mass in metal-rich ([Fe/H] > -1) GC candidates increases for a lower age 
threshold and moves closer to the dotted line that shows the distribution of
all star particles. However, we notice that the Auriga simulations, on average, 
do not form new stars with a metallicity below [Fe/H] = -1 more recent than 6 Gyr 
ago: the behaviour of Figure~\ref{fig:FeH} does not change for metallicities
below [Fe/H] = -1 when we change the age cut to 8 or 6 Gyr. The qualitative behaviour
of the median distribution of galactocentric radii (Figure~\ref{fig:Rgc}), on 
the other hand, is unaffected by lowering the age cut other than including
more star particles (more mass) which leads to a higher normalisation and
a higher mass ratio with respect to the observed GC systems of the MW and M31.
The qualitative behavour presented in Figure~\ref{fig:Au-FeHRgc-ratio} does not 
change when the age cut is lowered to 8 or 6 Gyr.
